### 2021-04-22 paper/ase21/conclusion.tex
[ASE21] Updated numbers

\section{Conclusion}\label{sec:conclusion}
Checking the correctness of ECMAScript is essential because an incorrect description
in ECMAScript can lead to wrong implementations of JavaScript engines. However,
since ECMAScript is annually released and developed in an open process, checking
its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
It is the first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  We also present
\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
using conditions of assertions and branches to improve the analysis precision.
We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
to perform type analysis for each version, and detected \inred{161} type-related specification bugs with
\inred{56.5}\% precision; \inred{91} out of \inred{161} reported bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the
committee confirmed them all.

>>>>

\section{Conclusion}\label{sec:conclusion}
Checking the correctness of ECMAScript is essential because an incorrect description
in ECMAScript can lead to wrong implementations of JavaScript engines. However,
since ECMAScript is annually released and developed in an open process, checking
its correctness becomes more labor-intensive and error-prone.  To alleviate the problem,
we propose $\tool$, a JavaScript Specification Type Analyzer using Refinement.
It is the first tool that performs \textit{type analysis} on JavaScript specifications and
detects specification bugs using a \textit{bug detector}.  We also present
\textit{condition-based refinement} for type analysis, which prunes out infeasible abstract states
using conditions of assertions and branches to improve the analysis precision.
We evaluated $\tool$ with all 864 versions in the official ECMAScript repository
for the last three years from 2018 to 2021.  It took \inred{137.3} seconds on average
to perform type analysis for each version, and detected \inred{157} type-related specification bugs with
\inred{59.2}\% precision; \inred{93} out of \inred{157} reported bugs are true bugs.
Among them, \inred{14} bugs are newly detected by $\tool$, and the
committee confirmed them all.

### 2021-04-22 paper/ase21/eval.tex
Removed unnecessary parentheses
[ASE21] Updated numbers

Figure~\ref{fig:stat} shows the statistics of the type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version, $\tool$ analyzed
\inred{1,689.6} functions on average.  Since ECMAScript has gradually evolved,
it analyzed \inred{1,490} functions for the first version in 2018
but analyzed \inred{1,863} functions in the latest.
$\tool$ analyzes functions with flow- and type-sensitive views.
On average, each version has \inred{91.2}K views and each function has
\inred{53.9}~views.

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{136.0} seconds with \inred{298.8}K iterations of
the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract}),
\inred{127.0} seconds for the type analysis (\stextsf{analyze}), and
\inred{0.7} seconds for the bug detection (\stextsf{detect}).

@@

We measured the analysis precision with the number of true bugs in
the type-related specification bugs detected by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{52.0}\%; \inred{92} out of \inred{177} detected bugs are true bugs.
The reference checker detected the most bugs with \inred{62.2}\% precision;
\inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{44} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found \inred{4} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
\inred{5} assertion failures (\stextsf{Assertion}) with \inred{16.1}\% precision.
Finally, the operand checker detected
\inred{2} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.

To understand the severity of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
how many days the bug lasts.  Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
Among \inred{92} true bugs, \inred{47} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{47} inherited bugs are created on January 1, 2018,
the average TTL is \inred{409.5} and the maximum TTL is \inred{1,164}.
All the bugs with the maximum TTL are inherited ones and they are all newly detected.

We manually investigated \inred{85} false-positive bugs to understand why
$\tool$ detected them.  Among them, \inred{30} bugs are due to extraction failure
of mechanized specifications caused by wrong writing styles.
Because ECMAScript is written in HTML, $\jiset$ extracts abstract algorithms
using the \code{emu-alg} HTML tag.  Unfortunately, several abstract algorithms are
defined with the opening tag \code{<emu-alg>} but without the closing tag \code{</emu-alg>},
which causes extraction failure of mechanized specifications leading
to false-positive bugs.  The remaining \inred{55} bugs are due to imprecise analysis.
We found that \inred{20} bugs are due to imprecise analysis of the
conditions of assertions and branches for specific function calls.
For example, consider the following algorithm step for \textbf{GetValue}:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
  \vspace*{-0.5em}
\end{figure} \noindent
Since \textbf{IsPropertyReference} always returns
$\code{false}$ when the $\code{Base}$ field of a given reference record is
$\nconst{unresolvable}$, the field access $V$.[[Base]] cannot be
$\nconst{unresolvable}$ on line 4.a.  However, because the type analysis
does not compute such information,
$\nconst{unresolvable}$ is also passed as the argument of \textbf{ToObject}.
We believe that an advanced refinement technique can
resolve this problem by pruning out infeasible field types depending on specific contexts.

@@

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{\footnotesize Operand} &
    \inred{2015-09-22} &
    \inred{1,996 days}\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took \inred{90.9} seconds with \inred{259.1}K
iterations on average.  For each version, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.98}x,
and \inred{1.41}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{30.4}\% to \inred{52.0}\% by removing \inred{122}
false-positive bugs and detecting \inred{one} more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement also significantly increased the analysis precision for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{28} and \inred{26} false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among \inred{92} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their TTLs.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,966 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

ES12-1 contains three bugs due to duplicated variable declarations
in three syntax-directed algorithms for the \jscode{case} block
of the \jscode{switch} statement:
\code{hasDuplicates} in \textbf{ContainsDuplicateLabels} and
\code{hasUndefinedLabels} in \textbf{ContainsUndefinedBreakTarget} and
\textbf{ContainsUndefinedContinueTarget}.
A \jscode{case} block optionally contains \jscode{case} clauses.
In the beginning of three algorithms,
\code{hasDuplicates} or \code{hasUndefinedLabels} is defined if the clauses exist.
However, because the same variable is defined again after the conditional steps,
three algorithms for \jscode{case} blocks
with \jscode{case} clauses always have the duplicated variable declaration bugs for
\code{hasDuplicates} (or \code{hasUndefinedLabels}).
Similarly, ES12-2 contains three bugs caused by the same reason in the
same abstract algorithms for the \jscode{try} statement.

>>>>

Figure~\ref{fig:stat} shows the statistics of the type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iterations, and
(d) the analysis time.  For each version, $\tool$ analyzed
\inred{1,696.6} functions on average.  Since ECMAScript has gradually evolved,
it analyzed \inred{1,491} functions for the first version in 2018
but analyzed \inred{1,864} functions in the latest.
$\tool$ analyzes functions with flow- and type-sensitive views.
On average, each version has \inred{92.0}K views and each function has
\inred{54.1}~views.

We measured the performance of $\tool$ with the worklist iteration number
and the analysis time.  For each version of ECMAScript,
$\tool$ took \inred{137.3} seconds with \inred{301.6}K iterations of
the worklist algorithm on average.  The average analysis time consists of \inred{8.0} seconds
for the specification extraction (\stextsf{extract}),
\inred{128.5} seconds for the type analysis (\stextsf{analyze}), and
\inred{0.8} seconds for the bug detection (\stextsf{detect}).

@@

We measured the analysis precision with the number of true bugs in
the type-related specification bugs detected by $\tool$.
As summarized in the \stextsf{refine} column of Table~\ref{table:precision}, the analysis precision
is \inred{59.2}\%; \inred{93} out of \inred{157} detected bugs are true bugs.
The reference checker detected the most bugs with \inred{80.8}\% precision;
\inred{17} unknown variables (\stextsf{UnknownVar}) and
\inred{46} duplicated variable declarations (\stextsf{DuplicatedVar}) are true bugs.
We found \inred{four} missing parameters (\stextsf{MissingParam}) with \inred{100.0}\% precision and
\inred{four} assertion failures (\stextsf{Assertion}) with \inred{12.9}\% precision.
Finally, the operand checker detected
\inred{two} non-numeric operand bugs (\stextsf{NoNumber}) with \inred{33.3}\% precision and
\inred{20} unchecked abrupt completion bugs (\stextsf{Abrupt}) with \inred{52.6}\% precision.

To understand the severity of the detected true bugs, we extended $\tool$ to
automatically extract when they are created and resolved in the ECMAScript
official repository.  A bug is \textit{created} when it exists
in a specific version but does not exist in its previous version, and
a bug is \textit{resolved} vice versa. The \textit{Time to Live (TTL)} of a bug denotes
how many days the bug lasts.  Figure~\ref{fig:ttl} illustrates the TTLs of true bugs;
Figure~\ref{fig:ttl}(a) depicts the TTLs sorted by creation time and
Figure~\ref{fig:ttl}(b) depicts the histogram of the TTLs in a logarithmic scale.
Among \inred{93} true bugs, \inred{48} bugs are \textit{inherited},
which means that they are created before 2018,
and \inred{14} bugs still exist in the latest ECMAScript, which are newly detected by $\tool$.
We discuss the details of \inred{14} newly found bugs in Section~\ref{sec:new-bug}.
Even though we assume that \inred{48} inherited bugs are created on January 1, 2018,
the average TTL is \inred{414.5} and the maximum TTL is \inred{1,164}.
All the bugs with the maximum TTL are inherited ones and they are all newly detected.

We manually investigated \inred{64} false-positive bugs to understand why
$\tool$ detected them.  Among them, \inred{17} bugs are due to extraction failure
of mechanized specifications caused by wrong writing styles.
Because ECMAScript is written in HTML, $\jiset$ extracts abstract algorithms
using the \code{emu-alg} HTML tag.  Unfortunately, several abstract algorithms are
defined with the opening tag \code{<emu-alg>} but without the closing tag \code{</emu-alg>},
which causes extraction failure of mechanized specifications leading
to false-positive bugs.  The remaining \inred{47} bugs are due to imprecise analysis.
We found that \inred{28} bugs are due to imprecise analysis of the
conditions of assertions and branches for specific function calls.
For example, consider the following algorithm step for \textbf{GetValue}:
\begin{figure}[H]
  \centering
  \vspace*{-0.5em}
  \includegraphics[width=0.7\columnwidth]{img/adv-refine-example}
  \vspace*{-0.5em}
\end{figure} \noindent
Since \textbf{IsPropertyReference} always returns
$\code{false}$ when the $\code{Base}$ field of a given reference record is
$\nconst{unresolvable}$, the field access $V$.[[Base]] cannot be
$\nconst{unresolvable}$ on line 4.a.  However, because the type analysis
does not compute such information,
$\nconst{unresolvable}$ is also passed as the argument of \textbf{ToObject}.
We believe that an advanced refinement technique can
resolve this problem by pruning out infeasible field types depending on specific contexts.

@@

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        Abrupt completions are used in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} \\ for \jscode{arguments} objects without any
        checks.
    } &
    \stextsf{\footnotesize Operand} &
    \inred{2015-12-16} &
    \inred{1,910 days}\\
  \end{tabular}
  }
  \vspace*{-1.5em}
\end{table*}

@@

For performance comparison, Figure~\ref{fig:performance-compare} presents the
iterations and analysis time without and with refinement.
Figures~\ref{fig:performance-compare}(a) and
\ref{fig:performance-compare}(c) are histograms of the iterations and analysis
time, respectively, and Figures~\ref{fig:performance-compare}(b) and
\ref{fig:performance-compare}(d) are scatter charts for their ratios.
Without refinement, the type analysis took \inred{91.9} seconds with \inred{261.5}K
iterations on average.  For each version, the number of iterations is increased
at least \inred{0.99}x, at most \inred{1.36}x, and \inred{1.16}x on average, and
the analysis time is increased at least \inred{1.05}x, at most \inred{1.99}x,
and \inred{1.41}x on average.

Table~\ref{table:precision} shows the analysis precision without refinement,
with refinement, and their difference.  The refinement improved the analysis
precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
false-positive bugs and detecting \inred{one} more true bug.  Among six
bug kinds, the most significant improvement is for non-numeric
operand bugs (\stextsf{NoNumber}) from \inred{3.1}\% to \inred{33.3}\%
by removing \inred{59} false-positive bugs.  The refinement technique
successfully prunes out non-numeric values for numeric types.
The refinement also significantly increased the analysis precision for unknown
variable bugs (\stextsf{UnknownVar}) and assertion failures
(\stextsf{Assertion}) by removing \inred{29} and \inred{25} false-positive bugs, respectively.
Because $\tool$ can precisely analyze callees of function invocations
without refinement, we found no improvement for missing
parameter bugs (\stextsf{MissingParam}).

@@

Among \inred{93} true bugs detected by $\tool$, \inred{14} are newly
detected and still exist in the latest version of ECMAScript.
Table~\ref{table:new-bug} summarizes the bugs, their
related JavaScript language features, and their TTLs.
Except for two bugs in ES12-8, all bugs were introduced in the initial
commit of the open development on September 22, 2015.
Thus, 12 newly detected bugs last for 1,966 days until March 9, 2021.
The two bugs in ES12-8 were created when a contributor introduced
the prefixes \textbf{?} and \textbf{!} on December 16, 2015, and they last for 1,910 days.
We reported the newly detected bugs to TC39, and all of them were
confirmed by the committee and will be fixed in ECMAScript 2022 (ES13).

ES12-1 contains three bugs due to duplicated variable declarations
in three syntax-directed algorithms for the \jscode{case} block
of the \jscode{switch} statement:
\code{hasDuplicates} in \textbf{ContainsDuplicateLabels} and
\code{hasUndefinedLabels} in \textbf{ContainsUndefinedBreakTarget} and
\textbf{ContainsUndefinedContinueTarget}.
A \jscode{case} block optionally contains \jscode{case} clauses.
In the beginning of three algorithms,
\code{hasDuplicates} or \code{hasUndefinedLabels} is defined if the clauses exist.
However, because the same variable is defined again after the conditional steps,
three algorithms for \jscode{case} blocks
with \jscode{case} clauses always have the duplicated variable declaration bugs for
\code{hasDuplicates} or \code{hasUndefinedLabels}.
Similarly, ES12-2 contains three bugs caused by the same reason in the
same abstract algorithms for the \jscode{try} statement.

### 2021-04-22 paper/ase21/intro.tex
[ASE21] Updated numbers

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{31.8}\% to \inred{56.5}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{161} type-related specification bugs with \inred{56.5}\% precision;
    \inred{91} out of \inred{161} bugs are true bugs.  Among them, $\tool$
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}

>>>>

The main contributions of this paper are as follows:
\begin{itemize}
  \item We present $\tool$, the first tool that performs a \textit{type
    analysis} on ECMAScript written in a natural language to check the correctness of JavaScript language
    specifications.  $\tool$ automatically detects type-related specification
    bugs such as unknown variables, duplicated variables, missing
    parameters, assertion failures, ill-typed operands, and unchecked
    abrupt completion bugs.
  \item We present a \textit{condition-based refinement} for type analysis of
    ECMAScript to reduce the number of false-positive bugs by enhancing the analysis
    precision.  We show that the refinement technique increases the analysis
    precision from \inred{33.0}\% to \inred{59.2}\% by removing \inred{122}
    false bugs and detecting \inred{one} more true bug.
  \item We demonstrate the practicality of $\tool$. It takes \inred{137.3}
    seconds on average to perform a type analysis for each version of ECMAScript and detected
    \inred{157} type-related specification bugs with \inred{59.2}\% precision;
    \inred{93} out of \inred{157} bugs are true bugs.  Among them, $\tool$
    newly detected \inred{14} bugs, and the ECMAScript committee confirmed them all.
\end{itemize}
